l

### 2023-09-15 resume/Resume.tex
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@7403e26c3bbc263873a1f2225d67d0b3e7be99bf 🚀
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@ecc266e08e824c5124385cbb8bc7f31f866fa001 🚀
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@7d29e351f5536af50d1566b3d2295e629d222916 🚀

\usepackage[T1]{fontenc}
\usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{etoolbox}[2011/01/03]
\usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,noerroretextools=true,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
\addbibresource{jason-gross.bib}
\DeclareBibliographyCategory{exclude}
\makeatletter
\@ifpackageloaded{etextools}{%
}{%
  \let\origifempty\ifempty
  \let\origforlistloop\forlistloop
  \undef\ifempty
  \usepackage{etextools}
  \let\eifempty\ifempty
  \let\ifempty\origifempty
  \let\forlistloop\origforlistloop
  \def\preetextools{\let\ifempty\eifempty}
}%
\makeatother
\begin{format}
  \employer{l}\dates{r}\\
  \title{l}\location{r} \\
  \body
\end{format}
\let\oldemployer=\employer
\let\oldtitle=\title
\renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
\renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

\newsectionwidth{1em}
\makeatletter
\pretocmd{\employer}{\vskip-\baselineskip}{}{}
\apptocmd{\@@section}{\vskip1.5\baselineskip\relax}{}{}
\makeatother
\resumewidth=7.5in

@@

\name{\LARGE \bf \parbox{\widthof{github.com/JasonGross}}{%
    \centering Jason Gross \\
    \vspace{0.2cm}
    \large \href{https://github.com/JasonGross/}{github.com/JasonGross} \\
    \href{https://people.csail.mit.edu/jgross/}{people.csail.mit.edu/jgross} \\
    $\left.\right.$ \\
    $\left.\right.$ \\%
}}

\vspace{5cm}

%\address{}%\textsc{Address}\\258 Prospect Street, Apt \# 1L\\Cambridge, MA 02139}
%\address{\textsc{Contact}\\\href{mailto:jgross@mit.edu}{jgross@mit.edu}\\(631) 790-8962}
\newcommand{\addressaswidth}[1]{\makebox[\widthof{\textsc{jgross@mit.edu}}][c]{#1}}
\address{\addressaswidth{\textsc{Contact}}\\\addressaswidth{\href{mailto:jgross@mit.edu}{jgross@mit.edu}}\\\addressaswidth{(631) 790-8962}}

@@

\section{\textsc{Research Interests}}
\begin{itemize}
\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
\end{itemize}

@@

\employer{Machine Intelligence Research Institute (MIRI)}
\dates{February 2021--Present}
\title{Research Staff}
\location{Berkeley, CA (remote)}
\begin{position}
  \begin{itemize}
  \item Performing self-directed research into topics in fundamental programming language theory and mathematics%, bringing insights and understanding back to my supervisor
  \end{itemize}
\end{position}

\employer{Coq Development Team, INRIA}
\dates{June 2021--Present}
\title{Core Team Member}
\location{Nantes, France (remote)}
\begin{position}
  \begin{itemize}
  \item Reported the plurality of all-time bugs in Coq (since 2012)
  \item Designed and engineered a bug minimizer for automatically producing minimized stand-alone test-cases from bug reports with automatic support for minimizing regressions in external projects tested by Coq CI
  \item Researching performance issues that impact scalability of automated verification
  \end{itemize}
\end{position}

\employer{MIT CSAIL}
\dates{September 2013--February 2021}
\title{PhD Researcher}
\location{Cambridge, MA}
\begin{position}
  \begin{itemize}
  \item Main Project: Fiat Cryptography (\href{https://github.com/mit-plv/fiat-crypto}{github.com/mit-plv/fiat-crypto})
  \item Fiat Cryptography is a developer tool to generate proven-correct cryptographic code. The project has wide industry adoption, including powering secure connections in Google Chrome and Firefox
  \item Lead development of one of the world's first algorithm-level-optimizing compilers
  \item Collaboratively implemented the tool; wrote backends to C, Go, Java, and JSON; managed development of backends to Rust and Zig
  \end{itemize}
\end{position}

@@

\section{\textsc{Programming Languages}}
\begin{itemize}
\item
  Proficient: Coq, %\onlymultitex{\cvlongfiles}{\TeX{} macro language, }
  Mathematica, git, Python, JavaScript, BASIC
\item
  Working knowledge: %\onlymultitex{\cvlongfiles}{\LaTeX{}, }
  C, C++, Agda, OCaml, Haskell, Scheme, HTML, CSS, Perl, Java
\item
  Basic knowledge: Matlab, Lean, Idris, Ruby, Go, Ur/Web, x86 Assembly
\end{itemize}

>>>>

\usepackage[T1]{fontenc}
\usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{etoolbox}[2011/01/03]
\expandafter\def\csname blx@noerroretextools\endcsname{}
\usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
\addbibresource{jason-gross.bib}
\DeclareBibliographyCategory{exclude}
\makeatletter
\@ifpackageloaded{etextools}{%
}{%
  \let\origifempty\ifempty
  \let\origforlistloop\forlistloop
  \undef\ifempty
  \usepackage{etextools}
  \let\eifempty\ifempty
  \let\ifempty\origifempty
  \let\forlistloop\origforlistloop
  \def\preetextools{\let\ifempty\eifempty}
}%
\makeatother
\begin{format}
  \employer{l}\dates{r}\\
  \title{l}\location{r} \\
  \body
\end{format}
\let\oldemployer=\employer
\let\oldtitle=\title
\renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
\renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

\newsectionwidth{1em}
\makeatletter
\def\firstemployerskip{\vskip-\baselineskip\def\employerskip{}}
\pretocmd{\employer}{\employerskip}{}{}
\apptocmd{\@@section}{\vskip1.5\baselineskip\relax\def\employerskip{\firstemployerskip}}{}{}
\makeatother
\resumewidth=7.5in

@@

\name{\LARGE Jason Gross\vspace{0.75cm}}
%\parbox{\textwidth}{%\widthof{github.com/JasonGross}}{%
%    {\LARGE \centering \textbf{Jason Gross}} \\
%    \vspace{0.2cm}
%    \large
%    \href{https://github.com/JasonGross/}{github.com/JasonGross} \\
%    \href{https://people.csail.mit.edu/jgross/}{people.csail.mit.edu/jgross} \\
%    $\left.\right.$ \\
%    $\left.\right.$ \\%
%}}

\address{\parbox{\textwidth}{%
  \href{mailto:jgross@mit.edu}{\large Email: \normalsize jgross@mit.edu}\hfill
  \href{https://people.csail.mit.edu/jgross/}{\large Website: \normalsize people.csail.mit.edu/jgross} \\
  \href{https://github.com/JasonGross/}{\large GitHub: \normalsize JasonGross}\hfill
  \href{https://scholar.google.com/citations?user=QouPlrMAAAAJ&hl=en}{\large Google Scholar: \normalsize QouPlrMAAAAJ}%
}%
}
%\address{}%\textsc{Address}\\258 Prospect Street, Apt \# 1L\\Cambridge, MA 02139}
%\address{\textsc{Contact}\\\href{mailto:jgross@mit.edu}{jgross@mit.edu}\\(631) 790-8962}
%\newcommand{\addressaswidth}[1]{\makebox[\widthof{\textsc{jgross@mit.edu}}][c]{#1}}
%\address{\addressaswidth{\textsc{Contact}}\\\addressaswidth{\href{mailto:jgross@mit.edu}{jgross@mit.edu}}\\\addressaswidth{(631) 790-8962}}

@@

\section{\textsc{Research Interests}}
\begin{itemize}
\item AI: Mechanistic Interpretability, Heuristic Arguments, Compact Proofs, Löb's Theorem
\item Security \& Engineering: Formal Verification, Cryptography, Bugs Infrastructure
\item Programming Languages: Type Theory, Performance, Proof Engines \& Automation
%
%\item Mechanistic Interpretability: Heuristic Arguments, Compact Proofs, Type Theory
%\item Security Engineering: Formal Verification, Cryptography, Performance Engineering
%\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
%%\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
\end{itemize}

@@

\employer{Special Project of ARC Theory}
\dates{August 2023--Present}
\title{Project Lead}
\location{Berkeley, CA}
\begin{position}
  \begin{itemize}
  \item Building the first machine-checked functional-correctness proofs of mechanistic interpretability arguments about transformers in Coq (\href{https://github.com/JasonGross/neural-net-coq-interp}{\texttt{github.com/JasonGross/neural-net-coq-interp}})
  \item Raised \$150k and leading an interdisciplinary team of ML researchers and mathematicians
  \end{itemize}
\end{position}

\employer{\mbox{Machine Intelligence Research Institute (MIRI)}}
\dates{February 2021--Present}
\title{Research Staff}
\location{Berkeley, CA (remote)}
\begin{position}
  \begin{itemize}
  \item Performing self-directed research into fundamental programming language theory and math%ematics%, bringing insights and understanding back to my supervisor
  \end{itemize}
\end{position}

\employer{Coq Development Team, INRIA}
\dates{June 2021--Present}
\title{Member of Core Team}
\location{Nantes, France (remote)}
\begin{position}
  \begin{itemize}
  \item Reported the plurality of all-time bugs in Coq (since 2012)
  \item Designed and engineered a bug report minimizer for automatically producing minimized standalone test-cases and minimizing regressions in external projects tested by Coq's CI
  \item Researching performance issues that impact scalability of automated verification
  \end{itemize}
\end{position}

\employer{MIT CSAIL}
\dates{September 2013--February 2021}
\title{PhD Researcher}
\location{Cambridge, MA}
\begin{position}
  \begin{itemize}
  \item Main Project: Fiat Cryptography (\href{https://github.com/mit-plv/fiat-crypto}{\texttt{github.com/mit-plv/fiat-crypto}})
  \item Fiat Cryptography is a developer tool to generate proven-correct cryptographic code, with wide industry adoption, powering the plurality of secure connections in Chrome and Firefox
  \item Lead development of one of the world's first algorithm-level-optimizing compilers
  \item Collaboratively implemented the tool; wrote backends to C, Go, Java, and JSON; managed development of backends to Rust and Zig
  \end{itemize}
\end{position}

@@

\section{\textsc{Programming Languages}}
\begin{itemize}
\item
  Proficient: Coq, Agda, Python, %\onlymultitex{\cvlongfiles}{\TeX{} macro language, }
  Mathematica, BASIC, \TeX{} macro language, git, JavaScript
\item
  Working knowledge: %\onlymultitex{\cvlongfiles}{\LaTeX{}, }
  C, C++, OCaml, Haskell, Scheme%/Racket
  , HTML, CSS, Perl, Bash, Java
\item
  Basic knowledge: MATLAB, Lean, Idris, Ruby, Go, Ur/Web, x86 Assembly, SQL, Batch
\end{itemize}
